A holomorphic approach to membranes and fivebranes

### 2022-06-29 fivebranes/fact.tex
all around

The observables of any theory in the BV formalism enhance to the structure of a factorization algebra on spacetime \cite{CG2}. 
Classically, if a theory in the BV formalism is described by a local $L_\infty$ algebra $\cL$ on spacetime $M$ then to an open set $U \subset M$ the factorization algebra of classical observables assigns the cochain complex
\[
\clie^\bu(\cL(U))
\]
which computes the Lie algebra cohomology of $\cL(U)$. 
The differential on this cochain complex is precisely the Chevellay--Eilenberg differential associated to the $L_\infty$ structure maps.

\begin{rmk}
The notion of a factorization algebra captures both the local and non-local operators in a quantum field theory. 
Indeed, from the data of a factorization algebra, one can recover local operators by the following formal construction. 
Let $\Obs$ be a factorization algebra on a smooth manifold $M$.
The classical \defterm{point observables} at $p \in M$ is the limit $\Obs(p) = \lim_{U \ni p} \Obs(U)$ where the limit runs over open sets $U \subset M$ containing $p$.
Generally this limit is difficult to compute, but for certain theories it is possible to give a concise expression which captures the essential features of the theory.
For example, in a holomorphic theory, the algebra of local operators is equivalent to the algebra generated by holomorphic derivatives of fields evaluated at a point \cite{CG2}.
\end{rmk}

At the quantum level this Chevellay--Eilenberg complex is deformed.
The BV formalism ...
Even in perturbation theory the full quantum behavior of the holomorphical-topological eleven-dimensional theory is an open question. 
We leave the problem to characterize the quantization to future work. 
\brian{add discussion}

In this section we will consider the classical factorization algebra of observables of our prototype for the minimal twist of eleven-dimensional supergravity given in \S \ref{s:twisted} which is defined on $S \times X$ where $X$ is a Calabi--Yau fivefold and $S$ a real oriented one-manifold. 
%In the \S \ref{s:twisted} we recalled a proposal for the description of the minimal twist of eleven-dimensional supergravity on $S \times X$. 
The primary object we used to describe the solutions of the equations of motion was the $\Z/2$ graded local $L_\infty$ algebra $\cL_{sugra}$, see \S \ref{s:Lsugra}. 
%As a graded vector space, observables on an open set $U \subset X \times S$ are thus $\cO(\cL_{sugra}(U)) = \Sym (\Pi \cL_{sugra})^\vee$.
%The differential is encoded by the $L_\infty$ structure which is exactly the Chevalley--Eilenberg differential.

@@

\subsection{The fivebrane decomposition}\label{s:resm5}

@@

This factorization algebra is not the factorization algebra associated to an ordinary sort of field theory on $Z$.
Nevertheless there is a subfactorization algebra which admits a natural grading so that each filtered component can be understood as such.
This grading is determined by a $\C^\times$ action on the fields of the eleven-dimensional theory on $\R \times X_Z$ which we now describe.

In a local chart $U \subset Z$ we can write a generic field of the eleven-dimensional theory on $\pi^{-1} U$ in coordinates as $f(t;w,z)$ where $t \in \R$ is the real coordinate, $w=(w_1,w_2)$ is the holomorphic fiber coordinate of the rank two bundle $X_Z$ over $Z$, and $z = (z_1,z_2,z_3)$ is a local holomorphic coordinate for $U \subset Z$.

@@

The main result of this section is the following.

@@

For each $n \in \Z$ and open set $U \subset Z$, let 
\[
\pi_* \cL_{sugra}(U)^{(n)} \subset \cL_{sugra}(\pi^{-1} U)
\]
be the weight $n$ eigenspace with respect to this $\C^\times$ action. 
%The $\C^\times$ action is compatible with the $\Z/2$ graded $L_\infty$ structure on $\cL_{sugra}$. 
Since the $n$th eigenspace is trivial when $n < -1$, we see that the product
\[
(\Bar{\pi}_* \cL_{sugra})(U) \define \prod_{n \geq -1} (\pi_*\cL_{sugra})(U)^{(n)}
\]
is equipped with the structure of a $\Z/2$ graded $L_\infty$ algebra.
In this way, the assignment 
\[
\Bar{\pi}_* \cL_{sugra} \colon U \mapsto (\Bar{\pi}_* \cL_{sugra})(U) 
\]
defines a sheaf of $\Z/2$ graded $L_\infty$ algebras on $Z$.

\begin{lem}
\label{lem:technical}
For each $n$, the sheaf of cochain complexes $U \mapsto \Bar{\pi}_* \cL_{sugra}(U)^{(n)}$ is quasi-isomorphic to one of the form
\[
\Omega^{0,\bu}(U, \cV_{fivebrane}^{(n)})
\]
for some finite rank super holomorphic vector bundle $\cV_{fivebrane}^{(n)}$ on $Z$.
For each $n$, the differential is of the form $\dbar + Q^{hol}$.
In particular, this endows $\Bar{\pi}_* \cL_{sugra}$ with the structure of a pro-vector bundle on $Z$. 
\end{lem}

\begin{proof}
In \S \ref{s:Lsugra} we introduced a holomorphic vector bundle $L_X$ defined on any Calabi--Yau five-fold $X$ whose sheaf of holomorphic sections was equipped with a $\Z/2$ graded $L_\infty$ structure. 
Here, we consider the Calabi--Yau fivefold $X = X_Z$ as defined above.
For any open subset $U \subset Z$ of the threefold the value of $\cL_{sugra}(\pi^{-1}U)$ as a sheaf of super vector spaces is 
\[
\Omega^\bu(\R) \otimes \Omega^{0,\bu}(p^{-1} U, L_{X_Z}),
\]
where $p \colon X_Z \to Z$ is the rank two bundle over $Z$. 
The one-ary structure map, or differential, is of the form $\d_{dR} + \dbar + Q^{hol}$ where $Q^{hol}$ is some odd holomorphic differential operator acting on sections of $L_{X_Z}$.

Since the de Rham complex of $\R$ is contractible we have a quasi-isomorphism of $L_\infty$ algebras
\[
\cL_{sugra}(\pi^{-1}U) \simeq \Omega^{0,\bu}(p^{-1} U, L_{X_Z})
\]
for every $U \subset Z$. 
Without loss of generality, we can assume that $U$ is a coordinate chart for the vector bundle $X_Z$ so that $X_Z|_U \cong U \times \C^2$ and where the bundle $L_{X_Z}$ splits as 
\[
L_{X_Z}|_{\pi^{-1} U} \cong L' \boxtimes L'' 
\]
where $L'$ is a holomorphic super vector bundle on $U$ and $L''$ is.a holomorphic vector on the fiber $\C^2$.
Then, we can further identify this with a Dolbeault complex of the form
\[
\Omega^{0,\bu} \left(U, L' \otimes \Omega^{0,\bu}(\C^2, L'') \right) . 
\]
By the Dolbeault Poincar\'e lemma applied to the holomorphic vector bundle $L''$ over $\C^2$,
\[
\Omega^{0,\bu} \left(U, L' \otimes M\right) 
\]
where we now interpret $L' \otimes M$ as an infinite rank bundle over $U \subset Z$---
the remaining differential is $\dbar_U + Q^{hol}$ where $Q^{hol}$ is a holomorphic differential operator.

With these simplifications, it suffices to show that the weight $n$ eigenspace of $L' \otimes M$ is finite rank over $U$ \brian{almost finished}
%we can fix a quasi-isomorphism $M \simeq \Omega^{0,\bu}(\C^2, L'')$ where $M$ is a 
\end{proof}

We explicitly describe the first few homogenous eigenspaces of $\Bar{\pi}_* \cL_{sugra}$.

@@

As an example, let us consider the weight $(-1)$ piece of the decomposition $\Omega^{0,\bu}(Z, \cV_{fivebrane}^{(-1)})$. 
We will show that 
\[
\cV_{fivebrane}^{(-1)} = K^{1/2}_Z \otimes \C^2 \oplus \cO_Z \oplus \Pi \T^*_Z 
\]
whose Dolbeault forms are equipped with the $\dbar$ operator and the $\del$ operator which takes functions to one-forms.

Explicitly weight zero summand $\cV_{fivebrane}^{(0)}$ consists of:
\begin{itemize}
\item 
Vector fields which are locally of the form $f^a(z) \del_{w_a}$ where $f^{a}(z)$ is a holomorphic function on $\C^3$.
Notice that these vector fields are automatically divergence-free.
Since $\del_{w_a}$ is treated as a section of $K^{1/2}_Z$ we see that these are local sections of $K^{1/2}_Z \otimes \C^2$. 
\item 
Next there are holomorphic functions (type $\beta$) and holomorphic $one$-forms (type $\gamma$) which do not depend on $w_a$. 
Since $\del$ is weight zero for the decomposition these forms combine to form the $\Z/2$ graded complex of sheaves
\[
\cO_Z \xto{\del} \Pi \Omega^{1,hol}_Z .
\]
\end{itemize}

@@

Particularly important for us will be the weight zero part $\Omega^{0,\bu}(Z, \cV_{fivebrane}^{(0)})$ of the $\Z/2$ graded $L_\infty$ algebra $\Bar{\pi}_* \cL_{sugra}$ which inherits the structure of a $\Z/2$ graded $L_\infty$ algebra.
When $Z = \C^3$ we will see that the global sections of this $\Z/2$ graded $L_\infty$ algebra is closely related to the exceptional Lie algebra $E(3|6)$ studied by Kac \cite{KacClass}.
%More precisely he weight zero piece is a local Lie algebra enhancement of this exceptional Lie algebra.

As a holomorphic vector bundle, we will see that $\cV_{fivebrane}^{(0)}$ is 
\[
\cV_{fivebrane}^{(0)} = \T_Z \oplus \lie{sl}(2) \otimes \cO_Z \oplus \Pi \left( \T^*_Z \otimes K^{-1/2}_Z \otimes \C^2 \right).
\]
The $L_\infty$ structure of $\cL_{sugra}$ endows the sheaf of sections of this holomorphic vector bundle with a Lie bracket which we will describe.

Explicitly, we enumerate all weight zero holomorphic sections:
\begin{itemize}
\item Vector fields which are locally of the form 
\[
\mu = f^i(z) \del_{z_i} - \frac12 \del_{z_i} f^i(z) w_a \del_{w_a}
\]
and vector fields which are locally of the form
\[
\mu = g(z) A^{ab} w_a \del_{w_b}.
\]
The condition that $\mu$ be divergence-free implies that $(A^{ab}) \in \lie{sl}(2)$.
We will identify the first such vector fields with sections of $\T_Z$ and the second such vector fields with sections of $\lie{sl}(2) \otimes \cO_Z$. 
\item Holomorphic functions of the form $\beta = w_a f(z)$ and holomorphic one-forms of the form $\gamma = g^{a}(z) \d w_a + h^{a} (z) w_a \d z$. 
Since $\del$ is weight zero, such sections are equipped with a differential 
\[
\Gamma^{hol}(Z, K^{-1/2}) \xto{D} \Pi \Gamma^{hol}(Z, K^{-1/2}) \oplus \Pi\Omega^{1,hol}(Z, K^{-1/2}) 
\]
which sends $w_a f(z) \mapsto (f(z) , w_a \del f (z))$. 
This $\Z/2$ graded complex of sheaves is clearly equivalent to $\Pi\Omega^{1,hol}(Z, K^{-1/2})$. 
\end{itemize}

The $L_\infty$ structure on $\Bar{\pi}_* \cL_{sugra}$ induces the structure of a local $\Z/2$ graded dg Lie algebra on $\Omega^{0,\bu}(Z, \cV_{fivebrane}^{(0)})$. 
The differential is simply $\dbar$. 
The Lie bracket is induced from a Lie algebra structure on holomorphic sections of $\cV_{fivebrane}^{(0)}$ which we can describe as follows:
\begin{itemize}
\item For $\Vect^{hol}(Z)$ there is the standard commutator of holomorphic vector fields. 
This acts on the sections of $\lie{sl}(2) \otimes \cO_Z$ and $\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2)$ by Lie derivative. 
\item On sections of $\lie{sl}(2) \otimes \cO_Z$ there is the matrix commutator. 
This acts on the odd part $\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2)$ where we view $\C^2$ as the fundamental $\lie{sl}(2)$ representation. 
\item Finally, and most interestingly, there is a bracket of the form
\[
\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2) \times \Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2) \to \Vect^{hol}(Z) \oplus \lie{sl}(2) \otimes \cO_Z 
\]
given in coordinates by
\[
[f^a(z) \d w_a , g^a \d w_b] = \left(??, ??\right) 
\]
\brian{finish}
\end{itemize}

\parsec[s:mainfact]

Since $\Bar{\pi}_* \cL_{sugra}$ is a pro-vector bundle with a compatible $L_\infty$ structure, the assignment 
\[
U\subset Z \mapsto \clie^\bu\left(\Bar{\pi}_* \cL_{sugra}(U)\right) 
\]
has the structure of a factorization algebra on the three-fold $Z$. 
We denote this factorization algebra by $\Bar{\pi}_* \Obs_{sugra}$.

@@

We briefly go through an analogous decomposition for membranes. 
For this, we fix a Riemann surface $C$ and consider the eleven-dimensional theory on $\R \times X_C$ where $X_C$ is the Calabi--Yau fivefold
\[
X_C = \text{Tot}(K_C^{1/4} \otimes \C^4),
\]
the total space of the rank four bundle $K_C^{1/4} \otimes \C^2$ over $C$.
Denote by 
\[
\pi \colon V \to \R \times C
\] 
the pullback of this vector bundle along the projection $\R \times C \to C$.
We can equivalently think of the eleven-manifold as the total space of the bundle $V$ over $\R \times C$. 
In this description, the twisted membranes will be supported along the zero section of $V$. 
The factorization algebra $\Obs_{sugra}$ on ${\rm Tot}(V)$ can be pushed forward along $\pi$ to a factorization algebra $\pi_* \Obs_{sugra}$ on $\R \times C$.

As in the fivebrane case, this is not the factorization algebra associated to an ordinary field theory on $\R \times C$.
Nevertheless there is a subfactorization algebra which admits a natural grading so that each filtered component can be understood as such.
This grading is determined by a (different) $\C^\times$ action on the fields of the eleven-dimensional theory on ${\rm Tot}(V) \cong \R \times X_C$ which we now describe.

@@

\begin{prop}
Let $\lie{g}$ be a Lie algebra and equip the associative dg algebra $\clie^\bu(\fg)$ with the augmentation induced by the tautological Lie map $0 \to \lie{g}$.
The Koszul dual of $\clie^\bu(\lie{g})$ with respect to this augmentation is equivalent to the universal enveloping algebra $U \fg$. 
\end{prop}

>>>>

The observables of any theory in the BV formalism have the structure of a factorization algebra on spacetime \cite{CG2}. 
Classically, if a theory in the BV formalism is described by a local $L_\infty$ algebra $\cL$ on spacetime $M$ then to an open set $U \subset M$ the factorization algebra of observables assigns the cochain complex
\[
\clie^\bu(\cL(U))
\]
which computes the Lie algebra cohomology of $\cL(U)$. 
The differential on this cochain complex is precisely the Chevellay--Eilenberg differential associated to the $L_\infty$ structure maps.

At the quantum level the factorization algebra of classical observables is deformed.
Perturbatively, Costello and Gwilliam use the BV formalism to give a systematic way to study quantization within the context of factorization algebras~\cite{CG2}. 
Even in perturbation theory, the full quantum behavior of the holomorphic-topological eleven-dimensional theory is an open question. 
We leave the problem to characterize the quantization to future work, and in this paper we do not address anything past tree-level in the bulk eleven-dimensional theory.

In this section we focus on the factorization algebra of classical observables of our prototype for the minimal twist of eleven-dimensional supergravity which we recalled in \S \ref{s:twisted}. 
This model is defined on any eleven-manifold $S \times X$ where $X$ is a Calabi--Yau fivefold and $S$ a real oriented one-manifold. 
%In the \S \ref{s:twisted} we recalled a proposal for the description of the minimal twist of eleven-dimensional supergravity on $S \times X$. 
The primary object we used to describe the solutions of the equations of motion was the $\Z/2$ graded local $L_\infty$ algebra $\cL_{sugra}$, see \S \ref{s:Lsugra}. 
%As a graded vector space, observables on an open set $U \subset X \times S$ are thus $\cO(\cL_{sugra}(U)) = \Sym (\Pi \cL_{sugra})^\vee$.
%The differential is encoded by the $L_\infty$ structure which is exactly the Chevalley--Eilenberg differential.

@@

\subsection{The fivebrane decomposition of twisted supergravity}\label{s:resm5}

@@

This factorization algebra is not the factorization algebra associated to an ordinary sort of field theory on $Z$.
Nevertheless there is a subfactorization algebra $\Bar{\pi}_* \Obs_{sugra}$ which admits a natural grading so that each filtered component can be understood as such. 
This grading is determined by looking at an eigenspace decomposition of a certain compact abelian group acting on the fields of the eleven-dimensional theory on $\R \times X_Z$ which we now describe.

One of the primary features of the factorization algebra $\Bar{\pi}_* \Obs_{sugra}$ is that it is of the form $\clie^\bu(\cG)$ where $\cG$ is a sheaf of $L_\infty$ algebras on $Z$ which is presented as the $C^\infty$-sections of a pro vector bundle.
To get a sense of the construction of this factorization algebra we take a brief excursion to a simpler construction related to branes in five-dimensional Chern--Simons theory.

\parsec[]

As we recalled in~\S \ref{??}, Costello's five-dimensional Chern--Simons theory is the result of applying the $\Omega$-background to $M$ theory on a Taub--NUT space.
In this setting, fivebranes which hit the tip of the Taub--NUT become chiral defects supported along a Riemann surface $C$ in the five-manifold. 
In analogy with the situation above, we take the five-manifold to be $\R \times {\rm Tot}(K_C)$ with the fivebranes wrapping the zero section.
Denote by $\Obs_{CS}$ the observables of five-dimensional Chern--Simons theory on $\R \times {\rm Tot}(K_C)$.
Let $\pi \colon \R \times {\rm Tot}(K_C) \to C$ be the natural projection and consider the factorization algebra $\pi_* \Obs_{CS}$ on $C$.

Notice that there is a $U(1)$ action on the fields of the five-dimensional theory induced by the $U(1)$ action on the five-manifold which scales the fiber of~$K_C$.
Using this we can look at the subfactorization algebra 
\beqn\label{eqn:taylor1a}
\Bar{\pi}_* \Obs_{CS} \subset \pi_* \Obs_{CS}
\eeqn
which to an open set $U \subset C$ assigns the complex of observables in $\Obs_{CS} (\pi^{-1} U)$ which are finite sums of integral eigenvectors for this $U(1)$ action.

For the rank one abelian gauge group, the space of fields of non-commutative Chern--Simons theory on $\R \times {\rm Tot}(K_C)$ is
\[
\Omega^\bu(\R) \otimes \Omega^{0,\bu}({\rm Tot}(K_C)) [1] .
\]
The interaction is encoded by the symplectic structure on ${\rm Tot}(K_C)$.
%For simplicity, let us assume that the canonical bundle on $C$ is trivializable. 
For $U \subset C$, the complex of observables is given in terms of the Lie algebra cohomology
\[
(\pi_* \Obs_{CS})(U) \simeq \clie^\bu \left(\Omega^{0,\bu}(p^{-1}U)\right)
\]
where $p \colon K_C \to C$.
If, moreover, $U$ is a trivializing cover then
\[
(\pi_* \Obs_{CS})(U) \simeq \clie^\bu \left(\Omega^{0,\bu}(C) \otimes \cO^{hol}(\C)\right) .
\]
On the other hand, we have
\[
(\Bar{\pi}_* \Obs_{CS})(U) \simeq \clie^\bu\left(\Omega^{0,\bu}(C) [[w]] \right) .
\]
Here, $w$ plays the role of a formal coordinate on the fiber of $K_C$ and $w^{k}$ as parametrizes the weight $k$ eigenspace---locally, $w$ is simply the one-form $\d z$.
Using this notation, the embedding \eqref{eqn:taylor1a} is induced by the Taylor series expansion map $\cO^{hol}(\C) \to \C[[w]]$.

\parsec[]

Let us return to the situation of a three-fold $Z$ in the eleven-manifold $\R \times \text{Tot}(K_{Z}^{1/2} \otimes \C^2)$. 
The construction of the restricted factorization algebra $\Bar{\pi}_* \Obs_{sugra}$ is completely similar to the simple case of five-dimensional Chern--Simons theory.

This time we consider the group $U(1) \times U(1)$ rotating the fibers of the rank two bundle $K_Z^{1/2} \otimes \C^2$. 
Using this we can define the subfactorization algebra 
\beqn\label{eqn:taylor1b}
\Bar{\pi}_* \Obs_{sugra} \subset \pi_* \Obs_{sugra}
\eeqn
which to an open set~$U \subset Z$ assigns the subcomplex of observables in~$\Obs_{sugra} (\pi^{-1} U)$ which are finite sums of integral eigenvectors for this $U(1) \times U(1)$ action.

By construction, the restricted factorization algebra is of the form
\[
\pi_*\Obs_{sugra} = \clie^\bu(\cG_Z) 
\]
where $\cG_Z$ is an infinite-rank local $L_\infty$ algebra on $Z$. 
Just as in the case of five-dimensional Chern--Simons theory, the embedding of factorization algebras \eqref{eqn:taylor1b} is induced by a partial Taylor expansion map
\[
\pi_* \cL_{sugra} \to \cG_Z .
\]

\parsec[s:cstarfive]

We now consider a particular decomposition of the factorization algebra $\Bar{\pi}_* \Obs_{sugra}$. 
In a local chart $U \subset Z$ we can write a generic field of the eleven-dimensional theory on $\pi^{-1} U$ in coordinates as $f(t;w,z)$ where $t \in \R$ is the real coordinate, $w=(w_1,w_2)$ is the holomorphic fiber coordinate of the rank two bundle $X_Z$ over $Z$, and $z = (z_1,z_2,z_3)$ is a local holomorphic coordinate for $U \subset Z$.

@@

The following proposition summarizes that this $\C^\times$-action is compatible with the $L_\infty$ structure on $\cL_{sugra}$.

@@

We consider this decomposition at the level of the local $L_\infty$ algebra $\cG_Z$.
Recall that the Chevalley--Eilenberg cochains of this local $L_\infty$ algebra is the restricted factorization algebra~$\Bar{\pi}_* \Obs_{sugra} = \clie^\bu(\cG_Z)$. 
For each $n \in \Z$ and open set $U \subset Z$, let 
\[
\cG_Z(U)^{(n)}\subset \cG_Z(U)
\]
be the weight $n$ eigenspace with respect to this $\C^\times$ action.
As a corollary of the proposition, we get a product decomposition 
\[
\cG_Z = \prod_{n \geq -1} \cG^{(n)} .
\]
In particular, we see that $\cG^{(0)}_Z$ is itself a local Lie algebra (that we will soon describe). 
Moreover, every $\cG^{(n)}$, $n \geq -1$ is a (local) module for this local Lie algebra.

We turn to explicitly describing the first few homogenous $\C^\times$-weights of~$\cG_Z$.

%The $\C^\times$ action is compatible with the $\Z/2$ graded $L_\infty$ structure on $\cL_{sugra}$. 
%Since the $n$th eigenspace is trivial when $n < -1$, we see that the product
%\[
%\cG_Z (U)  \prod_{n \geq -1} (\pi_*\cL_{sugra})(U)^{(n)}
%\]
%is equipped with the structure of a $\Z/2$ graded $L_\infty$ algebra.
%In this way, the assignment 
%\[
%\Bar{\pi}_* \cL_{sugra} \colon U \mapsto (\Bar{\pi}_* \cL_{sugra})(U) 
%\]
%defines a sheaf of $\Z/2$ graded $L_\infty$ algebras on $Z$.

%\begin{lem}
%\label{lem:technical}
%For each $n$, $\cG
%\[
%U \mapsto \Omega^{0,\bu}(U, \cV_{fivebrane}^{(n)})
%\]
%for some finite rank super holomorphic vector bundle $\cV_{fivebrane}^{(n)}$ on $Z$.
%For each $n$, the differential is of the form $\dbar + Q^{hol}$.
%In particular, this endows $\Bar{\pi}_* \cL_{sugra}$ with the structure of a pro-vector bundle on $Z$. 
%\end{lem}
%
%\begin{proof}
%In \S \ref{s:Lsugra} we introduced a holomorphic vector bundle $L_X$ defined on any Calabi--Yau five-fold $X$ whose sheaf of holomorphic sections was equipped with a $\Z/2$ graded $L_\infty$ structure. 
%Here, we consider the Calabi--Yau fivefold $X = X_Z$ as defined above.
%For any open subset $U \subset Z$ of the threefold the value of $\cL_{sugra}(\pi^{-1}U)$ as a sheaf of super vector spaces is 
%\[
%\Omega^\bu(\R) \otimes \Omega^{0,\bu}(p^{-1} U, L_{X_Z}),
%\]
%where $p \colon X_Z \to Z$ is the rank two bundle over $Z$. 
%The one-ary structure map, or differential, is of the form $\d_{dR} + \dbar + Q^{hol}$ where $Q^{hol}$ is some odd holomorphic differential operator acting on sections of $L_{X_Z}$. 
%
%Since the de Rham complex of $\R$ is contractible we have a quasi-isomorphism of $L_\infty$ algebras
%\[
%\cL_{sugra}(\pi^{-1}U) \simeq \Omega^{0,\bu}(p^{-1} U, L_{X_Z})
%\]
%for every $U \subset Z$. 
%Without loss of generality, we can assume that $U$ is a coordinate chart for the vector bundle $X_Z$ so that $X_Z|_U \cong U \times \C^2$ and where the bundle $L_{X_Z}$ splits as 
%\[
%L_{X_Z}|_{\pi^{-1} U} \cong L' \boxtimes L'' 
%\]
%where $L'$ is a holomorphic super vector bundle on $U$ and $L''$ is.a holomorphic vector on the fiber $\C^2$.
%Then, we can further identify this with a Dolbeault complex of the form
%\[
%\Omega^{0,\bu} \left(U, L' \otimes \Omega^{0,\bu}(\C^2, L'') \right) . 
%\]
%By the Dolbeault Poincar\'e lemma applied to the holomorphic vector bundle $L''$ over $\C^2$,
%\[
%\Omega^{0,\bu} \left(U, L' \otimes M\right) 
%\]
%where we now interpret $L' \otimes M$ as an infinite rank bundle over $U \subset Z$---
%the remaining differential is $\dbar_U + Q^{hol}$ where $Q^{hol}$ is a holomorphic differential operator.
%
%With these simplifications, it suffices to show that the weight $n$ eigenspace of $L' \otimes M$ is finite rank over $U$ \brian{almost finished}
%%we can fix a quasi-isomorphism $M \simeq \Omega^{0,\bu}(\C^2, L'')$ where $M$ is a 
%\end{proof}

@@

The first non trivial case is the weight $(-1)$ piece $\cG_Z^{(-1)}$.
We will show that
$\cG_Z^{(-1)}$ is equivalent as an abelian local Lie algebra to one of the form $\Omega^{0,\bu}(Z, \cV^{(-1)})$ where $\cV^{(-1)}$ is the holomorphic vector bundle
\[
\cV^{(-1)} = K^{1/2}_Z \otimes \C^2 \oplus \cO_Z \oplus \Pi \T^*_Z .
\]
The Dolbeault forms are equipped with the natural $\dbar$ operator and the $\del$ operator which takes functions to one-forms.

Explicitly weight $(-1)$ summand $\cV^{(-1)}$ consists of:
\begin{itemize}
\item 
Vector fields which are locally of the form $f^a(z) \del_{w_a}$ where $f^{a}(z)$ is a holomorphic function on $Z$.
Notice that these vector fields are automatically divergence-free.
Since $\del_{w_a}$ is treated as a section of $K^{1/2}_Z$ we see that these are local sections of $K^{1/2}_Z \otimes \C^2$. 
\item 
Next there are holomorphic functions (type $\beta$) and holomorphic $one$-forms (type $\gamma$) which do not depend on $w_a$. 
Since $\del$ is weight zero for the decomposition these forms combine to form the $\Z/2$ graded complex of sheaves
\[
\cO_Z \xto{\del} \Pi \Omega^{1,hol}_Z .
\]
\end{itemize}

@@

Particularly important for us will be the weight zero summand $\cG_Z^{(0)}$.
Again, as a local Lie algebra it is equivalent to one of the form $\Omega^{0,\bu}(Z, \cV^{(0)})$.
When $Z = \C^3$ we will see that the global sections of this $\Z/2$ graded $L_\infty$ algebra is closely related to the exceptional Lie algebra $E(3|6)$ studied by Kac \cite{KacClass}.
%More precisely he weight zero piece is a local Lie algebra enhancement of this exceptional Lie algebra.

The holomorphic vector bundle $\cV^{(0)}$ is 
\[
\cV^{(0)} = \T_Z \oplus \lie{sl}(2) \otimes \cO_Z \oplus \Pi \left( \T^*_Z \otimes K^{-1/2}_Z \otimes \C^2 \right).
\]
The local $L_\infty$ structure of $\cL_{sugra}$ endows the Dolbeault complex of this holomorphic vector bundle with a local Lie algebra structure.
The differential turns out to be the natural $\dbar$ operator.
We describe the bracket below.

Explicitly, we enumerate all holomorphic sections of $\cV^{(0)}$:
\begin{itemize}
\item Vector fields which are locally of the form 
\[
\mu = f^i(z) \del_{z_i} - \frac12 \del_{z_i} f^i(z) w_a \del_{w_a}
\]
and vector fields which are locally of the form
\[
\mu = g(z) A^{ab} w_a \del_{w_b}.
\]
The condition that $\mu$ be divergence-free implies that $(A^{ab}) \in \lie{sl}(2)$.
We identify the first such vector fields with sections of $\T_Z$ and the second such vector fields with sections of $\lie{sl}(2) \otimes \cO_Z$. 
\item Holomorphic functions of the form $\beta = w_a f(z)$ and holomorphic one-forms of the form $\gamma = g^{a}(z) \d w_a + h^{a} (z) w_a \d z$. 
Since $\del$ is weight zero, such sections are equipped with a differential 
\[
\Gamma^{hol}(Z, K^{-1/2}\otimes \C^2) \xto{D} \Pi \Gamma^{hol}(Z, K^{-1/2} \otimes \C^2) \oplus \Pi\Omega^{1,hol}(Z, K^{-1/2}\otimes \C^2) 
\]
which sends $w_a f(z) \mapsto (f(z) , w_a \del f (z))$. 
This $\Z/2$ graded complex of sheaves is equivalent to $\Pi\Omega^{1,hol}(Z, K^{-1/2}\otimes \C^2)$. 
\end{itemize}

The Lie bracket on $\cG_Z^{(0)}$ is induced from a Lie algebra structure on holomorphic sections of $\cV^{(0)}$ which we can describe as follows:
\begin{itemize}
\item For $\Vect^{hol}(Z)$ there is the standard commutator of holomorphic vector fields. 
This acts on the sections of $\lie{sl}(2) \otimes \cO_Z$ and $\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2)$ by Lie derivative. 
\item On sections of $\lie{sl}(2) \otimes \cO_Z$ there is the matrix commutator. 
This acts on the odd part $\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2)$ where we view $\C^2$ as the fundamental $\lie{sl}(2)$ representation. 
\item Finally, and most interestingly, there is a bracket of the form
\[
\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2) \times \Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2) \to \Vect^{hol}(Z) \oplus \lie{sl}(2) \otimes \cO_Z 
\]
given in coordinates by
\begin{multline}
[f^{ai}(z) w_a \d z_i, g^{bj} (z) w_b \d z_j] = \ep_{ijk} \ep_{ab} f^{ai} (z) g^{bj}(z) \del_{z_k} \\ + \ep_{ijk} \ep_{bc}  \del_{z_k} f^{ai}(z) g^{bj}(z) w_a \del_{w_c} + \ep_{ijk} \ep_{ac} f^{ai}(z) \del_{z_k} g^{bj}(z) w_b \del_{w_c} .
\end{multline}
The top line is a holomorphic vector field on~$Z$ and the bottom line is a $\lie{sl}(2)$-valued holomorphic function on~$Z$.
\end{itemize}

%\parsec[s:mainfact]
%
%Since $\cG_Z$ is a pro-vector bundle with a compatible $L_\infty$ structure, the assignment 
%\[
%U\subset Z \mapsto \clie^\bu\left(\Bar{\pi}_* \cL_{sugra}(U)\right) 
%\]
%has the structure of a factorization algebra on the three-fold $Z$. 
%We denote this factorization algebra on $Z$ by $\Obs_{sugra}|_Z$.

@@

We briefly highlight an analogous construction of the restricted factorization algebra which is natural from the point of view of membranes.
Recall that in the twist we are considering the worldvolume theory of membranes is a three-dimensional partially topological-holomorphic field theory which exist on a product $\R \times C$ where $C$ is a Riemann surface.

We consider the eleven-dimensional theory on $\R \times X_C$ where $X_C$ is the Calabi--Yau fivefold
\[
X_C = \text{Tot}(K_C^{1/4} \otimes \C^4),
\]
the total space of the rank four bundle $K_C^{1/4} \otimes \C^4$ over $C$.
Denote by 
\[
\pi \colon V \to \R \times C
\] 
the pullback of this vector bundle along the projection $\R \times C \to C$.
We can equivalently think of the eleven-manifold as the total space of the bundle $V$ over $\R \times C$. 
In this description, the twisted membranes will be supported along the zero section of $V$. 
The factorization algebra $\Obs_{sugra}$ on ${\rm Tot}(V)$ can be pushed forward along $\pi$ to a factorization algebra $\pi_* \Obs_{sugra}$ on $\R \times C$.

As in the fivebrane case, this is not the factorization algebra associated to an ordinary field theory on $\R \times C$.
Nevertheless there is a subfactorization algebra $\Bar{\pi}_* \Obs_{sugra}$ which admits a natural grading so that each filtered component can be understood as such.

To construct this factorization algebra we consider the action of the compact torus $U(1)^{\times 4}$ which rotates the fibers of the bundle $K_C^{1/4} \otimes \C^4$.
We let $\Bar{\pi}_* \Obs_{sugra}$ be the factorization algebra on $\R \times C$ consisting of observables which are finite sums of integral eigenvectors for this group action.
Again, we find that $\Bar{\pi}_* \Obs_{sugra}$ is of the form $\clie^\bu(\cG_{\R \times C})$ for some $\infty$ sheaf of $L_\infty$ algebras $\cG_{\R \times C}$ on $\R \times C$ which is the sections of a pro vector bundle.

Analogous to the decomposition determined by the $\C^\times$ action considered in \ref{s:cstarfive}, there is a decomposition of $\cG_{\R \times C}$ determined by a (different) $\C^\times$ acting on the fields of the eleven-dimensional theory on ${\rm Tot}(V) \cong \R \times X_C$.

@@

\begin{prop}
Let $\lie{g}$ be a Lie algebra and equip the associative (and commutative) dg algebra $\clie^\bu(\fg)$ with the augmentation induced by the tautological homomorphism $0 \to \lie{g}$.
The Koszul dual of $\clie^\bu(\lie{g})$ with respect to this augmentation is equivalent to the universal enveloping algebra $U \fg$. 
\end{prop}
